---
title: "Study 5 (in progress)"
author: "SMK"
date: "07/06/2022"
output: rmdformats::material
---

***
# Packages Used

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(apaTables)
library(gt)
library(sjPlot)
library(rmdformats)
library(psych)
library(gtsummary)
library(ggplot2)
library(ggcorrplot)
library(QuantPsyc)
library(lavaan)
library(semPlot)
library(BaylorEdPsych)
library(tidySEM)
library(sjmisc)
library(broom)
library(knitr)
library(effects)
library(multcomp)
library(haven)
```

***
# Dataset
```{r warning=FALSE, message=FALSE}
setwd("C:\\Users\\sarah\\Documents\\PhD\\All data files")
poriginaldata <- read.csv("Study 5 Prolific.csv",header =TRUE)
goriginaldata <-read.csv("Study 5 Gen pop.csv",header =TRUE)
```

# Variables
```{r warning=FALSE, message=FALSE}
names(poriginaldata)
```

```{r warning=FALSE, message=FALSE}
names(goriginaldata)
```
***
# Data Cleaning 

## Step 1: Remove ineligible participants {.tabset}
(Prolific - this is anyone who's residency is less than 5 years, General - this is anyone who answered no to screen)
Unnecessary variables will then be removed.

### Prolific
```{r warning=FALSE, message=FALSE}
ptidydata <- poriginaldata[!(poriginaldata$Residency< 5),]
pdata<-ptidydata[-c(1:4,6:13)]
```
### General
```{r warning=FALSE, message=FALSE}
gtidydata <- goriginaldata[!(goriginaldata$Screen> 4),]
gdata<-gtidydata[-c(1:4,6:12)]
```

## Step 2: Combine data files and create composite variables
```{r warning=FALSE, message=FALSE}
alldata <- rbind(pdata,gdata)

SAtotal<-alldata$SA1 + alldata$SA2 + alldata$SA3 + alldata$SA4
LItotal<-alldata$LI1 + alldata$LI2 + alldata$LI3 + alldata$LI4 + alldata$LI5 
NRtotal<-alldata$NR1 + alldata$NR2 + alldata$NR4 + alldata$NR5
MTtotal<-alldata$MT1 + alldata$MT2 + alldata$MT3 + alldata$MT4 + alldata$MT5 + alldata$MT6
RMAtotal<-SAtotal+LItotal+NRtotal+MTtotal
fulldata<-cbind(alldata, SAtotal, LItotal, NRtotal, MTtotal, RMAtotal)
```

## Step 3: Remove cases with over 7% missing data
```{r warning=FALSE, message=FALSE}
cleandata<-fulldata
percentmiss<- function(x){sum(is.na(x))/length(x)*100}
missing= apply(cleandata, 1, percentmiss)
table(missing)
nomissing<-cleandata[missing<7,]
summary(is.na(nomissing))
```

## Step 4: Remove failed attention checks
```{r warning=FALSE, message=FALSE}
cleanerdata<-nomissing
Fail1<-(cleanerdata$Attn1!=6)
Fail2<-(cleanerdata$Attn2!=3)
Fail3<-(cleanerdata$Attn3!=4)
Totalfail<-(Fail1 & Fail2 & Fail3)

cleanestdata<-cleanerdata[-Totalfail,]
```

## Step 5: Remove multivariate outliers 
This analysis will ignore demographic variables and individual scale items, plus the RMA composite score for an accurate mahalanobis distance score
```{r warning=FALSE, message=FALSE}
mahal<- mahalanobis(cleanestdata[,c(34,50:60)], colMeans(cleanestdata[,c(34,50:60)],na.rm = TRUE),cov(cleanestdata[,c(34,50:60)], use = "pairwise.complete.obs"))
cutoff<- qchisq(.999,ncol(cleanestdata[,c(34,50:60)]))
cutoff
summary(mahal<cutoff)
```

```{r warning=FALSE, message=FALSE}
finaldata<-cleanestdata[mahal<cutoff,]

```

***

# Additional variables

## Condition
```{r warning=FALSE, message=FALSE}
finaldata$Con_time[is.na(finaldata$Con_time)]<-0
Condition<- ifelse(finaldata$Con_time>"0",0,1)
Condition[is.na(Condition)] <- 1
```

## Consent
```{r warning=FALSE, message=FALSE}
C1dum<-ifelse(finaldata$C1 == '6', 1, 0)
C2dum<-ifelse(finaldata$C2 == '3', 1, 0)
C3dum<-ifelse(finaldata$C3 == '4', 1, 0)
C4dum<-ifelse(finaldata$C4 == '2', 1, 0)
C5dum<-ifelse(finaldata$C5 == '2', 1, 0)
C6dum<-ifelse(finaldata$C6 == '3', 1, 0)
C7dum<-ifelse(finaldata$C7 == '1', 1, 0)
C8dum<-ifelse(finaldata$C8 == '4', 1, 0)
C9dum<-ifelse(finaldata$C9 == '3', 1, 0)
C10dum<-ifelse(finaldata$C10 == '1', 1, 0)
ConsentScore<- C1dum+C2dum+C3dum+C4dum+C5dum+C6dum+C7dum+C8dum+C9dum+C10dum

```

## Subset with outliers
```{r}
cleanestdata$Con_time[is.na(cleanestdata$Con_time)]<-0
Conditions<- ifelse(cleanestdata$Con_time>"0",0,1)
Conditions[is.na(Conditions)] <- 1
C1<-ifelse(cleanestdata$C1 == '6', 1, 0)
C2<-ifelse(cleanestdata$C2 == '3', 1, 0)
C3<-ifelse(cleanestdata$C3 == '4', 1, 0)
C4<-ifelse(cleanestdata$C4 == '2', 1, 0)
C5<-ifelse(cleanestdata$C5 == '2', 1, 0)
C6<-ifelse(cleanestdata$C6 == '3', 1, 0)
C7<-ifelse(cleanestdata$C7 == '1', 1, 0)
C8<-ifelse(cleanestdata$C8 == '4', 1, 0)
C9<-ifelse(cleanestdata$C9 == '3', 1, 0)
C10<-ifelse(cleanestdata$C10 == '1', 1, 0)
ConsentTotal<- C1+C2+C3+C4+C5+C6+C7+C8+C9+C10
fulldf<-cbind(cleanestdata, Conditions, ConsentTotal)
fulldata<-fulldf[,c(34:39,50:63)]
```


## Subsets for analysis
```{r}
df<-cbind(finaldata, Condition, ConsentScore)
write_sav(df, "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data\\Rfinaldata.sav")
write.csv(df, "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data\\finaldataR5.csv")
dataset<-df[,c(34:39,50:63)]
data<-df[,c(34:39,50:63)]
datas<-df[,c(2:7,16,18:21,24:29,50:63)]
control<-data[(data$Condition==0),]
intervention<-data[(data$Condition==1),]
```

Final dataset has 394 participants
Full dataset has 410 participants

## Factoring
```{r warning=FALSE, message=FALSE}
dataset$Gender= factor(dataset$Gender,levels = c(1,2,3,4,5,6),labels = c("male","female","trans male", "trans female", "genderqueer", "different identity"))
dataset$Ethnicity= factor(dataset$Ethnicity,levels = c(1:14),labels = c("White Caucasian","White Mexican","White Sephardic Jew", "East Asian", "South Asian", "Middle Eastern", "Native American", "Latino/Hispanic", "Caribbean", "Black British", "African", "Black African American", "Mixed", "Other"))
dataset$Sexuality= factor(dataset$Sexuality,levels = c(1,2,3,4,5),labels = c("heterosexual","bisexual","homosexual", "asexual", "other sexuality"))
dataset$Victim_known= factor(dataset$Victim_known,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know victim","friend or family member victim", "victim themself"))
dataset$False_acc_known= factor(dataset$False_acc_known,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know accused","friend or family member accused", "accused themself"))
dataset$Verdict= factor(dataset$Verdict,levels = c(0,1),labels = c("Not Guilty", "Guilty"))
dataset$Likert_verdict= factor(dataset$Likert_verdict,levels = c(1,2,3,4,5,6,7),labels = c("Completely unlikely", "Moderately unlikely", "Slightly unlikely", "Neither likely nor unlikely", "Slightly likely", "Moderately likely", "Completely likely"))
dataset$Credibility= factor(dataset$Credibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely incredible", "Moderately incredible", "Slightly incredible", "Neither credible nor incredible", "Slightly credible", "Moderately credible", "Completely credible"))
dataset$Responsibility= factor(dataset$Responsibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely unresponsible", "Moderately unresponsible", "Slightly unresponsible", "Neither responsible nor unresponsible", "Slightly responsible", "Moderately responsible", "Completely responsible"))
dataset$Empathy= factor(dataset$Empathy,levels = c(1,2,3,4,5),labels = c("Not at all", "Slightly", "Moderately", "A lot", "Completely"))
dataset$Condition=factor(dataset$Condition,levels= c(0,1),labels= c("Control", "Intervention"))
```
***
# Descriptive Statistics

```{r}
dataset %>%
  dplyr::select(Gender, Ethnicity, Sexuality, Victim_known, False_acc_known )%>%
  tbl_summary(
    label= list(Gender ~ "Gender",Ethnicity ~ "Ethnicity", Sexuality~ "Sexual Orientation", Victim_known~ "Rape victim known", False_acc_known~ "False accusation known")) %>%
  modify_caption("<div style='text-align: left;font-weight: bold'> Table 1.<br> Demographic Statistics</div>")
```

```{r}
describe(data[,c(7:18,20)], fast=T)
```

```{r}
describe.by(data[,c(7:20)], fast=T, group ="Condition")
```

## Age
```{r warning=FALSE, message=FALSE}
dataset%>%
  summarise(Variable= "Age",
            Mean=mean(Age, na.rm = TRUE),
            Median= median(Age, na.rm = TRUE),
            SD= sd(Age, na.rm = TRUE))
```

## Victim 
```{r warning=FALSE, message=FALSE}
v<-ggplot(data=dataset, aes(Victim_known))
v+geom_histogram(stat="Count", aes(fill=as.factor(Victim_known))) +
  theme_classic(base_size = 10,base_family = "Times") + 
  labs( title = "Victim known", x = "Victim known", y= "Frequency" ) +
   theme(axis.text.x = element_text(angle = 20, hjust=1)) +
  scale_fill_brewer(palette="PRGn")
```


## False allegations 
```{r warning=FALSE, message=FALSE}
f<-ggplot(data=dataset, aes(False_acc_known))
f+ geom_histogram(stat="Count",  aes(fill=as.factor(False_acc_known))) +
    theme_classic(base_size = 10,base_family = "Times") + 
    labs( title = "False Accusation Known", x = "False Accusation Known", y=  "Frequency" ) +
    theme(axis.text.x = element_text(angle = 20, hjust=1)) +
    scale_fill_brewer(palette="YlGnBu")
```



## U-IRMA Reliability analysis 
```{r warning=FALSE, message=FALSE}
fullscale<- df[,c(2:8, 10,11, 13:16, 18:21, 24:29)]
alpha(fullscale)
correctscale<- df[,c(2:5,8,10,11, 13:16, 18,20,21, 24:29)]
alpha(correctscale)
```

# Dependent variables {.tabset}

## Dichotomous Verdict
```{r warning=FALSE, message=FALSE}
table(dataset$Verdict)
Ver<-table(dataset$Verdict)
percent<-Ver/467
percent
barplot(Ver, col= grey.colors(2), main = "Verdict")
```

## Likert Verdict
```{r warning=FALSE, message=FALSE}

lv<-ggplot(data=dataset, aes(Likert_verdict))
lvg<-lv+  geom_histogram(stat="Count", aes(fill=as.factor(Likert_verdict))) +
  theme_classic(base_size = 10,base_family = "Times") + ylim(c(0,140))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs( title = "Likert Verdict", x = "Likelihood of defendent's guilt", y= "Frequency")+ 
  scale_fill_brewer(palette="Greys")
```

### Credibility
```{r warning=FALSE, message=FALSE}
dataset%>%
  dplyr::select(Credibility)%>%
  tbl_summary()

cr<-ggplot(data=dataset, aes(Credibility))
crg<-cr+  geom_histogram(stat="Count", aes(fill=as.factor(Credibility))) +
  theme_classic(base_size = 10,base_family = "Times") + 
  scale_y_continuous( breaks= seq(0,150,25)) +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs( title = "Credibility", x = "Credibility Rating", y= "Frequency" )+
  scale_fill_brewer(palette="Greys")

```

### Responsibility
```{r warning=FALSE, message=FALSE}
dataset%>%
  dplyr::select(Responsibility)%>%
  tbl_summary()

re<-ggplot(data=dataset, aes(Responsibility))
regraph<-re+  geom_histogram(stat="Count", aes(fill=as.factor(Responsibility))) +
  theme_classic(base_size = 10,base_family = "Times") + ylim(c(0,120))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs(title = "Responsibility", x = "Responsibility rating", y= "Frequency" )+
  scale_fill_brewer(palette="Greys", direction = -1)

```

### Empathy
```{r warning=FALSE, message=FALSE}
dataset%>%
  dplyr::select(Empathy)%>%
  tbl_summary()

em<-ggplot(data=dataset, aes(Empathy))
emg<-em+  geom_histogram(stat="Count", aes(fill=as.factor(Empathy))) +
  theme_classic(base_size = 10,base_family = "Times") + ylim(c(0,120))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs(title = "Empathy", x = "Empathy rating", y= "Frequency" ) +
  scale_fill_brewer(palette="Greys")

```

***
# Correlation Matrix
```{r}
cordata<-data[,c(3:6,8:18,20)]
tab_corr(cordata, p.numeric = TRUE, triangle = "lower")
```

## Scatterplot Matrix
```{r warning=FALSE, message=FALSE}
corr<-round(cor(data),2)
ggcorrplot(corr,type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle",
           colors= c("deepskyblue4","white","green4"),
           ggtheme=theme_classic (base_family = "Times", base_size = 10)) 
```

***

# Mean Comparison

Comparing samples
```{r warning=FALSE, message=FALSE}
options(scipen = 999)
lapply(data[,c(3:6)], function(x)t.test(x~Condition,var.eq=F, options(digits=5)))
```

Comparing outcomes
```{r}
options(scipen=999)

conttest<-lapply(data[,c(8:18,20)],function(x)t.test(x~dataset$Condition,var.eq=F))
contable<-map_df(conttest, broom::tidy, .id="var")
print.data.frame(contable)

tvalues<-contable$statistic
eta<-function(x){(x*x)/(x*x+(n-1))}
n=393
eta(tvalues)

```

Effect size
```{r warning=FALSE, message=FALSE}
tvalues<-c(-3.41,-2.01,-1.11,-2.64,2.74,-2.87,0.89,-4.06)
eta<-function(x){(x*x)/(x*x+(n-1))}
n=393
eta(tvalues)
```

```{r}
sapply(control,sd)
```
```{r}
sapply(intervention,sd)
```


## Chi-square
### Gender
```{r warning=FALSE, message=FALSE}
sex<-factor(data$Gender,levels = c(1,2),labels = c( "Male","Female"))
chitable<-table(sex,dataset$Condition)
barplot(chitable, beside=T, legend=T)
chisq.test(chitable, correct = T)

```

### Verdict
```{r warning=FALSE, message=FALSE}
chitable2<-table(dataset$Verdict,dataset$Condition)
chitable2
barplot(chitable2, beside=T, legend=T)
chisq.test(chitable2, correct = T)
```

***

# Logistic regression 

## Control condition
```{r warning=FALSE, message=FALSE}
options(scipen = 999)
controlmodel<-glm(Verdict~ SAtotal + LItotal + NRtotal + Credibility + Responsibility + Empathy, family = binomial(link = logit), data= control)
summary(controlmodel)
controlmodel%>%
  tbl_regression(exponentiate = TRUE)%>% add_vif()
```

The test below checks whether the change in errors is significantly less for the model without predictors. 
```{r warning=FALSE, message=FALSE}
options(scipen = 999)
chidiff<-controlmodel$null.deviance-controlmodel$deviance
dfdiff<-controlmodel$df.null-controlmodel$df.residual
chidiff
dfdiff
pchisq(chidiff, dfdiff, lower.tail = F)
```

```{r warning=FALSE, message=FALSE}
PseudoR2(controlmodel)
```

```{r warning=FALSE, message=FALSE}
correctc<-controlmodel$fitted.values
binarycorrectc<-ifelse(correctc>0.5,1,0)
binarycorrectc<-factor(binarycorrectc, levels=c(0,1), labels=c("Not Predicted","Predicted"))
table(control$Verdict, binarycorrectc)
```

Creating equal number for intervention group (i.e. removing 4)
```{r}
evenintervention<-intervention[c(1:195),]
```



## Intervention condition
```{r warning=FALSE, message=FALSE}
options(scipen = 999)
intmodel<-glm(Verdict~ SAtotal + LItotal + NRtotal + Credibility + Responsibility + Empathy, family = binomial(link = logit), data= intervention)
summary(intmodel)
intmodel%>%
  tbl_regression(exponentiate = TRUE)%>% add_vif()
```

```{r}
options(scipen = 999)
chidiffint<-intmodel$null.deviance-intmodel$deviance
dfdiffint<-intmodel$df.null-intmodel$df.residual
chidiffint
dfdiffint
pchisq(chidiffint, dfdiffint, lower.tail = F)

```

```{r}
PseudoR2(intmodel)
```

```{r}
correcti<-intmodel$fitted.values
binarycorrecti<-ifelse(correcti>0.5,1,0)
binarycorrecti<-factor(binarycorrecti, levels=c(0,1), labels=c("Not Predicted","Predicted"))
table(intervention$Verdict, binarycorrecti)

```



# Hierarchical regression

## Control condition

### Step 1
```{r warning=FALSE, message=FALSE}
regoutput1c=lm(Likert_verdict~Gender+Confidence,control)
summary(regoutput1c)
lm.beta(regoutput1c)
apa.reg.table(regoutput1c)

```

## Step 2
```{r warning=FALSE, message=FALSE}
regoutput2c=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal,control)
summary(regoutput2c)
lm.beta(regoutput2c)
apa.reg.table(regoutput2c)
```

## Step 3
```{r warning=FALSE, message=FALSE}
regoutput3c=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal+Credibility+Responsibility+Empathy,control)
summary(regoutput3c)
lm.beta(regoutput3c)
```

### Regression Model comparison
```{r warning=FALSE, message=FALSE}
anova(regoutput1c,regoutput2c)
anova(regoutput1c,regoutput2c,regoutput3c)
apa.reg.table(regoutput3c)
```

## Intervention condition
### Step 1
```{r}
regoutput1i=lm(Likert_verdict~Gender+Confidence,intervention)
summary(regoutput1i)
lm.beta(regoutput1i)
apa.reg.table(regoutput1i)
```

### Step 2
```{r}
regoutput2i=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal,intervention)
summary(regoutput2i)
lm.beta(regoutput2i)
apa.reg.table(regoutput2i)

```

### Step 3
```{r}

regoutput3i=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal+Credibility+Responsibility+Empathy,intervention)
summary(regoutput3i)
lm.beta(regoutput3i)
```

### Regression model comparison
```{r}
anova(regoutput1i,regoutput2i)
anova(regoutput1i,regoutput2i,regoutput3i)
apa.reg.table(regoutput3i)
```

***

# Moderation

## Variables and dataset
```{r}
Cond<-rec(data$Condition, rec="0=-0.5;1=0.5")
LI_c<-data$LItotal-mean(data$LItotal)
SA_c<-data$SAtotal-mean(data$SAtotal)
NR_c<-data$NRtotal-mean(data$NRtotal)
Condition<-data$Condition
Cred<-data$Credibility
Resp<-data$Responsibility
Emp<-data$Empathy

LI_cond<-LI_c*Condition
SA_cond<-SA_c*Condition
NR_cond<-NR_c*Condition

```


```{r}
moddata<-data[,c(11:16,19)]
moddata<-cbind(moddata, LI_c, SA_c, NR_c, LI_cond, SA_cond, NR_cond)
```

## Credibility 
```{r}
mod1<-' 
Credibility~a1*LI_c
Credibility~a2*Condition
Credibility~a3*LI_cond
'
```

```{r}
set.seed(2020)

modfit1<-sem(mod1,data=moddata,se="bootstrap", bootstrap=5000, ordered = c("Condition"), estimator= "DWLS")
```

Model 1 analysis
```{r}
summary (modfit1, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modfit1,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```




## Responsibility
```{r}
mod2<-' 
Responsibility~a1*SA_c
Responsibility~a2*Condition
Responsibility~a3*SA_cond
'
```

```{r}
set.seed(2021)

modfit2<-sem(mod2,data=moddata,se="bootstrap", bootstrap=5000, ordered = c("Condition"), estimator= "DWLS")
```

Model 2 analysis
```{r}
summary (modfit2, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modfit2,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```







## Empathy

```{r}
mod3<-' 
Empathy~a1*NR_c
Empathy~a2*Condition
Empathy~a3*NR_cond
'
```

```{r}
set.seed(2022)

modfit3<-sem(mod3,data=moddata,se="bootstrap", bootstrap=5000, ordered = c("Condition"), estimator= "DWLS")
```

Model 3 analysis
```{r}
summary (modfit3, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modfit3,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```
***
# Mediation model group comparision
```{r warning=FALSE}
groupmed1 <- '
    # direct effect
      Verdict ~ c(cg1, cg2)*LItotal
  
    # mediation
      Credibility ~ a(ag1,ag2)*LItotal
      Verdict ~ b(bg1,bg2)*Credibility
  
    # indirect effect (a*b)
      abg1 := ag1*bg1 
      abg2 := ag2*bg2 

    # total effect
      totalg1 := cg1 + (ag1*bg1)
      totalg2 := cg2 + (ag2*bg2)
'

groupcredmed <- sem(groupmed1, data = data, ordered = "Verdict", group= "Condition", se = "bootstrap", bootstrap = 1000, estimator= "DWLS")
```

```{r}
summary(groupcredmed, standardize = TRUE, rsquare = TRUE, fit.measures= TRUE)
```

```{r}
all.constraints<- 'ag1 == ag2
                  bg1 == bg2
                  cg1 == cg2'

lavTestWald(groupcredmed, constraints = all.constraints)
```

```{r}
lavTestWald(groupcredmed, constraints = "ag1==ag2")
```

```{r}
lavTestWald(groupcredmed, constraints = "bg1==bg2")
```

```{r}
lavTestWald(groupcredmed, constraints = "cg1==cg2")
```

Responsibility
```{r warning=FALSE}
groupmed2 <- '
    # direct effect
      Verdict ~ c(crg1, crg2)*SAtotal
  
    # mediation
      Responsibility ~ a(arg1,arg2)*SAtotal
      Verdict ~ b(brg1,brg2)*Responsibility
  
    # indirect effect (a*b)
      rabg1 := arg1*brg1 
      rabg2 := arg2*brg2 

    # total effect
      totalg1 := crg1 + (arg1*brg1)
      totalg2 := crg2 + (arg2*brg2)
'

grouprespmed <- sem(groupmed2, data = data, ordered = "Verdict", group= "Condition", se = "bootstrap", bootstrap = 1000, estimator= "DWLS")
```

```{r}
summary(grouprespmed, standardize = TRUE, rsquare = TRUE, fit.measures= TRUE)
```

```{r}
all.constraints<- 'arg1 == arg2
                  brg1 == brg2
                  crg1 == crg2'

lavTestWald(grouprespmed, constraints = all.constraints)
```

```{r}
lavTestWald(grouprespmed, constraints = "arg1==arg2")
```

```{r}
lavTestWald(grouprespmed, constraints = "brg1==brg2")
```

```{r}
lavTestWald(grouprespmed, constraints = "crg1==crg2")
```


empathy

```{r warning=FALSE}
groupmed3 <- '
    # direct effect
      Verdict ~ c(ceg1, ceg2)*NRtotal
  
    # mediation
      Empathy ~ a(aeg1,aeg2)*NRtotal
      Verdict ~ b(beg1,beg2)*Empathy
  
    # indirect effect (a*b)
      eabg1 := aeg1*beg1 
      eabg2 := aeg2*beg2 

    # total effect
      etotalg1 := ceg1 + (aeg1*beg1)
      etotalg2 := ceg2 + (aeg2*beg2)
'

groupempmed <- sem(groupmed3, data = data, ordered = "Verdict", group= "Condition", se = "bootstrap", bootstrap = 1000, estimator= "DWLS")
summary(groupempmed, standardize = TRUE, rsquare = TRUE, fit.measures= TRUE)
```

```{r}
all.constraints<- 'aeg1 == aeg2
                  beg1 == beg2
                  ceg1 == ceg2'

lavTestWald(groupempmed, constraints = all.constraints)
```

```{r}
lavTestWald(groupempmed, constraints = "aeg1==aeg2")
```

```{r}
lavTestWald(groupempmed, constraints = "beg1==beg2")
```

```{r}
lavTestWald(groupempmed, constraints = "ceg1==ceg2")
```
***

# Moderated-Mediation analyses
```{r}
Cred_c<-data$Credibility-mean(data$Credibility)
Resp_c<-data$Responsibility-mean(data$Responsibility)
Emp_c<-data$Empathy-mean(data$Empathy)
Verdict<-data$Verdict
LikVer<-data$Likert_verdict
Cond<-rec(data$Condition, rec="0=-0.5;1=0.5")
IntLI<-LI_c*Cond
IntSA<-SA_c*Cond
IntNR<-NR_c*Cond
meddata<-cbind(moddata, Cred_c, Resp_c, Emp_c, Verdict, LikVer, Cond, IntLI, IntSA, IntNR)
```

```{r}
write.csv(meddata,"C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data\\meddata.csv")
```


## Credibility 

```{r}
med1<-' #a path
Cred_c~a1*LI_c
Cred_c~a2*Cond
Cred_c~a3*IntLI

#b path
Verdict~b1*Cred_c

#c prime path
Verdict~cp*LI_c

#Modmed index
b1a3:=b1*a3

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5'
```


fit model
```{r}
set.seed(1432)
modmed1<-sem(med1,data=meddata,se="bootstrap", bootstrap=5000, ordered = c("Verdict", "Condition"), estimator= "DWLS")
```

```{r}
summary (modmed1, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modmed1,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```
## Modmed plots
```{r}
summary(data$LItotal)
sd(data$LItotal)
credlm <- lm(Credibility ~ LItotal * Condition, data = data)

mod_table1 <- effect(term = "LItotal:Condition", mod = credlm, x.var = "LItotal", xlevels = list(Condition = c(0,1), LI_c=seq(6,40,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))
condition <- Condition %>% recode(`0` = "Control", `1` = "Intervention")
kable(mod_table1)
```


```{r}
ssc<-meddata %>% 
  ggplot(mapping = aes(x = LItotal, y = Credibility)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = mod_table1, mapping = aes(x = LItotal, y = fit, linetype = condition)) +
  geom_ribbon(data = mod_table1, mapping = aes(x = LItotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(moddata$LI_c)) +
  scale_y_continuous(breaks = pretty(moddata$Credibility)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  labs(x = "Total LI scores", y= "Credibility") +
  theme(legend.position = "right")

ssc
ssplot1<-ssc
ggsave("ssplot1.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```
```{r}
resplm <- lm(Responsibility ~ SAtotal * Condition, data = data)
mod_table2 <- effect(term = "SAtotal:Condition", mod = resplm, x.var = "SAtotal", xlevels = list(Condition = c(0,1), SAtotal=seq(4,22,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

kable(mod_table2)
```
```{r}
ssr<-meddata %>% 
  ggplot(mapping = aes(x = SAtotal, y = Responsibility)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = mod_table2, mapping = aes(x = SAtotal, y = fit, linetype = condition)) +
  geom_ribbon(data = mod_table2, mapping = aes(x = SAtotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(moddata$SA_c)) +
  scale_y_continuous(breaks = pretty(moddata$Responsibility)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "right")

ssr
ssplot2<-ssr
ggsave("ssplot2.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```
```{r}
emplm <- lm(Empathy ~ NRtotal * Condition, data = moddata)
mod_table3 <- effect(term = "NRtotal:Condition", mod = emplm, x.var = "NRtotal", xlevels = list(Condition = c(0,1), NRtotal=seq(4,19,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

kable(mod_table3)
```
```{r}
sse<-meddata %>% 
  ggplot(mapping = aes(x = NRtotal, y = Empathy)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = mod_table3, mapping = aes(x = NRtotal, y = fit, linetype = condition)) +
  geom_ribbon(data = mod_table3, mapping = aes(x = NRtotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(moddata$NR_c)) +
  scale_y_continuous(breaks = pretty(moddata$Empathy)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "right")

sse
ssplot3<-sse
ggsave("ssplot3.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```

```{r}
cvblm <- lm(Verdict ~ Credibility * Condition, data = data)
cvblm_table <- effect(term = "Credibility:Condition", mod = cvblm, x.var = "Credibility", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot4<-data %>% 
  ggplot(mapping = aes(x = Credibility, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = cvblm_table, mapping = aes(x = Credibility, y = fit, linetype = condition)) +
  geom_ribbon(data = cvblm_table, mapping = aes(x = Credibility, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$Credibility)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot4.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```


```{r}
rvblm <- lm(Verdict ~ Responsibility * Condition, data = data)
rvblm_table <- effect(term = "Responsibility:Condition", mod = rvblm, x.var = "Responsibility", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot5<-data %>% 
  ggplot(mapping = aes(x = Responsibility, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = rvblm_table, mapping = aes(x = Responsibility, y = fit, linetype = condition)) +
  geom_ribbon(data = rvblm_table, mapping = aes(x = Responsibility, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$Responsibility)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot5.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```


```{r}
evblm <- lm(Verdict ~ Empathy * Condition, data = data)
evblm_table <- effect(term = "Empathy:Condition", mod = evblm, x.var = "Empathy", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot6<-data %>% 
  ggplot(mapping = aes(x = Empathy, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = evblm_table, mapping = aes(x = Empathy, y = fit, linetype = condition)) +
  geom_ribbon(data = evblm_table, mapping = aes(x = Empathy, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$Empathy)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot6.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```

```{r}
livlm <- lm(Verdict ~ LItotal * Condition, data = data)
livlm_table <- effect(term = "LItotal:Condition", mod = livlm, x.var = "LItotal", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot7<-data %>% 
  ggplot(mapping = aes(x = LItotal, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = livlm_table, mapping = aes(x = LItotal, y = fit, linetype = condition)) +
  geom_ribbon(data = livlm_table, mapping = aes(x = LItotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$LItotal)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot7.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```


```{r}
savlm <- lm(Verdict ~ SAtotal * Condition, data = data)
savlm_table <- effect(term = "SAtotal:Condition", mod = savlm, x.var = "SAtotal", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot8<-data %>% 
  ggplot(mapping = aes(x = SAtotal, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = savlm_table, mapping = aes(x = SAtotal, y = fit, linetype = condition)) +
  geom_ribbon(data = savlm_table, mapping = aes(x = SAtotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$SAtotal)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot8.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```

```{r}
nrvlm <- lm(Verdict ~ NRtotal * Condition, data = data)
nrvlm_table <- effect(term = "NRtotal:Condition", mod = nrvlm, x.var = "NRtotal", xlevels = list(Condition = c(0,1))) %>%
  as_tibble %>%
  mutate(condition = Condition %>% recode(`0` = "Control", `1` = "Intervention"))

ssplot9<-data %>% 
  ggplot(mapping = aes(x = NRtotal, y = Verdict)) +
  geom_point(mapping = aes(color = condition)) +
  geom_line(data = nrvlm_table, mapping = aes(x = NRtotal, y = fit, linetype = condition)) +
  geom_ribbon(data = nrvlm_table, mapping = aes(x = NRtotal, y = fit, ymin = lower, ymax = upper, fill = condition), alpha = 0.5) +
  scale_x_continuous(breaks = pretty(data$NRtotal)) +
  scale_y_continuous(breaks = pretty(data$Verdict)) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic(base_size = 10) +
  theme(legend.position = "top")
ggsave("ssplot9.jpg",path= "C:\\Users\\sarah\\Documents\\PhD\\Study 4 Data" )
```

```{r}
library(gridExtra)
grid.arrange(ssplot1, ssplot2, ssplot3, ssplot4, ssplot5, ssplot6, ssplot7, ssplot8, ssplot9, ncol=3, nrow = 3)
```


## Responsibility

```{r}
med2 <- '
#a path
Resp_c~a1*SA_c
Resp_c~a2*Cond
Resp_c~a3*IntSA

#b path
Verdict~b1*Resp_c

#c prime path
Verdict~cp*SA_c

#Modmed index
b1a3:=b1*a3  

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5
'
```

```{r}
set.seed(1543)
modmed2<-sem(med2,data=meddata,se="bootstrap", bootstrap=5000, ordered = c("Verdict", "Condition"), estimator= "DWLS")
```

```{r}
summary (modmed2, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modmed2,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```

## Empathy

```{r}
med3 <- '
#a path
Emp_c~a1*NR_c
Emp_c~a2*Cond
Emp_c~a3*IntNR

#b path
Verdict~b1*Emp_c

#c prime path
Verdict~cp*NR_c

#Modmed index
b1a3:=b1*a3  

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5
'
```

```{r}
set.seed(1654)
modmed3<-sem(med3,data=meddata,se="bootstrap", bootstrap=5000, ordered = c("Verdict", "Condition"), estimator= "DWLS")
```

```{r}
summary (modmed3, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
parameterestimates(modmed3,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
```

# Multigroup SEM
```{r}
Confidence<-datas$Confidence
Confscale<-scale(Confidence, center=TRUE, scale=TRUE)
semdata<-cbind(datas, Confscale)
```

```{r}
SEMmodel<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4
NR=~1*NR1+NR2+NR4+NR5

#regression equations
Verdict~Credibility+Responsibility+Empathy
Sentence~Verdict
Credibility~Empathy

Credibility~LI
Responsibility~SA
Empathy~NR

#Estimating endogenous variables covariance
SA~~LI+NR
LI~~NR

'
```

```{r}
set.seed(1816)
MGSEMmodel<-sem(SEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition")
summary(MGSEMmodel, fit.measures=TRUE)
parameterestimates(MGSEMmodel, standardized = T)
```


## config
```{r}
set.seed(1816)
configmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition")
fitMeasures(configmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```
## metric
```{r warning=FALSE}
set.seed(1816)
metricmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition",  group.equal = "loadings")
fitMeasures(metricmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```
## scalar
```{r warning=FALSE}
set.seed(1816)
scalarmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition",  group.equal =c("intercepts", "loadings"))
fitMeasures(scalarmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```

## strict
```{r warning=FALSE}
set.seed(1816)
strictmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition",  group.equal =c("intercepts", "loadings", "residuals"))
fitMeasures(strictmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```

## compare
```{r}
lavTestLRT(configmodel, metricmodel, scalarmodel,strictmodel)
```

